\subsection{Mapping Ranges Type}

Since \ANLOpenCL/ is a port of the Josua Tippetts' C++ library
\url{http://accidentalnoise.sourceforge.net/index.html} the same documentation
can be used for the mapping ranges.

The struct \ANLOpenCLTypeIndex{SMappingRanges} is defined with the fields
\begin{itemize}
\item \ANLOpenCLType{mapx0, mapy0, mapz0, mapx1, mapy1, mapz1} and
\item \ANLOpenCLType{loopx0, loopy0, loopz0, loopx1, loopy1, loopz1}
\end{itemize}

\subsection{Mapping Ranges Functions}

\subsubsection{Create Mapping Ranges Functions}

\index{create\_ranges\_default}\index{create\_ranges\_map2D}\index{create\_ranges\_map3D}
\begin{lstlisting}[caption={Definition of create ranges functions},label={lst:create_ranges_definition},language=OpenCL]
struct SMappingRanges create_ranges_default();
struct SMappingRanges create_ranges_map2D(REAL x0, REAL x1, REAL y0, REAL y1);
struct SMappingRanges create_ranges_map3D(REAL x0, REAL x1, REAL y0, REAL y1, REAL z0, REAL z1)
\end{lstlisting}

\begin{lstlisting}[caption={Example for create ranges functions},label={lst:create_ranges_example},language=OpenCL]
struct SMappingRanges ranges = create_ranges_default();
//
struct SMappingRanges ranges = create_ranges_map2D(-10, 10, -10, 10);
//
struct SMappingRanges ranges = create_ranges_map3D(-10, 10, -10, 10, 0, 1);
\end{lstlisting}

Defined in \ANLOpenCLTypeIndex{imaging.h}.
The first function creates a default \ANLOpenCLType{SMappingRanges} from -1 to 1.
The other functions create \ANLOpenCLType{SMappingRanges} with the specified ranges.

\subsubsection{Set Mapping Ranges Functions}

\index{set\_ranges\_default}\index{set\_ranges\_map2D}\index{set\_ranges\_map3D}
\begin{lstlisting}[caption={Definition of set ranges functions},label={lst:set_ranges_definition},language=OpenCL]
struct SMappingRanges set_ranges_default(struct SMappingRanges *const ranges);
struct SMappingRanges set_ranges_map2D(struct SMappingRanges *const ranges, REAL x0, REAL x1, REAL y0, REAL y1);
struct SMappingRanges set_ranges_map3D(struct SMappingRanges *const ranges, REAL x0, REAL x1, REAL y0, REAL y1, REAL z0, REAL z1);
\end{lstlisting}

\begin{lstlisting}[caption={Example for set ranges functions},label={lst:set_ranges_example},language=OpenCL]
struct SMappingRanges ranges;
set_ranges_default(&ranges);
//
set_ranges_map2D(&ranges, -10, 10, -10, 10);
//
set_ranges_map3D(&ranges, -10, 10, -10, 10, 0, 1);
\end{lstlisting}

Defined in \ANLOpenCLTypeIndex{imaging.h}.
The first function sets a default \ANLOpenCLType{SMappingRanges} from -1 to 1.
The other functions sets \ANLOpenCLType{SMappingRanges} with the specified ranges.

\subsubsection{Mapping Functions}

\index{map2D}\index{map2DNoZ}
\begin{lstlisting}[caption={Definition of mapping functions},label={lst:mapping_definition},language=OpenCL]
void* map2D(void *out, calc_seamless calc_seamless, struct SMappingRanges ranges, size_t width, size_t height, REAL z);
void* map2DNoZ(void *out, calc_seamless_no_z calc_seamless, struct SMappingRanges ranges, size_t width, size_t height);
\end{lstlisting}

\begin{lstlisting}[caption={Example for mapping functions},label={lst:mapping_example},language=OpenCL]
struct SMappingRanges ranges = create_ranges_map2D(-10, 10, -10, 10);
map2D(coord, calc_seamless_none, ranges, 1024, 1024, 0);
\end{lstlisting}

Defined in \ANLOpenCLTypeIndex{imaging.h}.
Creates the mapping ranges for the width and height. Different seamless functions are supported.
The coordinates must have the correct size that is dependent on the seamless function used.
For the \ANLOpenCLType{map2D} function the following seamless functions are available and the
coordinates type must be used:

\begin{itemize}
\item \ANLOpenCLTypeIndex{calc\_seamless\_none} coordinates must be of \ANLOpenCLType{vector3}
\item \ANLOpenCLTypeIndex{calc\_seamless\_x} coordinates must be of \ANLOpenCLType{vector4}
\item \ANLOpenCLTypeIndex{calc\_seamless\_y} coordinates must be of \ANLOpenCLType{vector4}
\item \ANLOpenCLTypeIndex{calc\_seamless\_z} coordinates must be of \ANLOpenCLType{vector4}
\item \ANLOpenCLTypeIndex{calc\_seamless\_xy} coordinates must be of \ANLOpenCLType{vector8}
\item \ANLOpenCLTypeIndex{calc\_seamless\_xz} coordinates must be of \ANLOpenCLType{vector8}
\item \ANLOpenCLTypeIndex{calc\_seamless\_yz} coordinates must be of \ANLOpenCLType{vector8}
\item \ANLOpenCLTypeIndex{calc\_seamless\_xyz} coordinates must be of \ANLOpenCLType{vector8}
\end{itemize}

For the \ANLOpenCLType{map2DNoZ} function the following seamless functions are available and the
coordinates type must be used:

\begin{itemize}
\item \ANLOpenCLTypeIndex{calc\_seamless\_no\_z\_none} coordinates must be of \ANLOpenCLType{vector2}
\item \ANLOpenCLTypeIndex{calc\_seamless\_no\_z\_x} coordinates must be of \ANLOpenCLType{vector3}
\item \ANLOpenCLTypeIndex{calc\_seamless\_no\_z\_y} coordinates must be of \ANLOpenCLType{vector3}
\item \ANLOpenCLTypeIndex{calc\_seamless\_no\_z\_z} coordinates must be of \ANLOpenCLType{vector4}
\item \ANLOpenCLTypeIndex{calc\_seamless\_no\_z\_xy} coordinates must be of \ANLOpenCLType{vector4}
\item \ANLOpenCLTypeIndex{calc\_seamless\_no\_z\_xz} coordinates must be of \ANLOpenCLType{vector8}
\item \ANLOpenCLTypeIndex{calc\_seamless\_no\_z\_yz} coordinates must be of \ANLOpenCLType{vector8}
\item \ANLOpenCLTypeIndex{calc\_seamless\_no\_z\_xyz} coordinates must be of \ANLOpenCLType{vector8}
\end{itemize}

\subsubsection{Scale To Range}

\index{scaleToRange}
\begin{lstlisting}[caption={Definition of scaleToRange function},label={lst:scale_to_range_definition},language=OpenCL]
REAL* scaleToRange(REAL *data, size_t count, REAL min, REAL max, REAL low, REAL high);
\end{lstlisting}

\begin{lstlisting}[caption={Example for scaleToRange function. The data will be scaled to fit between 0 and 1.},label={lst:scale_to_range_example},language=OpenCL]
scaleToRange(data, count, min, max, 0, 1);
\end{lstlisting}

Defined in \ANLOpenCLTypeIndex{imaging.h}.
Scales the values in data to the range between low and high.
The data is modified by this function.
 
